Bioverse: Origins of Life

### 2024-05-28 src/tex/ms.tex
adapt figure for only one hypothesis

\subsection{Hydrothermal vents}
e.g., Russell+2010
...
The hydrothermal vents scenario requires a direct contact of an ocean and the planetary mantle/crust.
This requirement is not met on an ocean world with large amounts of water, where the water pressure on the ocean floor is high enough to form high-pressure ices (Noack+2016). % TODO Sleep et al., 2011? Sobotta et al., 2020?
\todo[inline]{see discussion in Kite \& Ford 2018 Sect. 6.4}
\todo[inline]{SR: The sealing away of the planetary interior from the ocean due to high-pressure ice layers is a common assumption for water world exoplanets (in addition to the references above, see e.g. Hu et al. 2021). I'm not convinced it is correct, because of relatively recent evidence showing the possibility of molecular assimitation into such ices and subsequent transport, e.g., https://iopscience.iop.org/article/10.1088/0004-637X/769/1/29/meta, https://iopscience.iop.org/article/10.3847/1538-4357/acb49a/meta, https://iopscience.iop.org/article/10.3847/1538-4357/aa5cfe/meta (I'm sure there are other workers in this area, this is just the group with which I am familiar). Exoplaneteers mostly uniformly accept this proposition, so it's not an unreasonable assumption if you want to run with it so long as its acknowledged and caveated reasonably; I'm just highlighting this for your attention so that you can make an informed decision. }

@@

%\subsection{Origins of Life Hypotheses}
...
\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/hypotheses.pdf}
        \caption{Origins of Life scenarios, their predictions on exoplanet observables, and derived population-level hypotheses.}
        \label{fig:hypotheses}
    \end{centering}
\end{figure*}
Figure~\ref{fig:hypotheses} lists the hypotheses derived from the predictions of each OOL scenario.
...

>>>>

%\subsection{Hydrothermal vents}
A widely regarded origins-of-life scenario is that abiogenesis happens in hydrothermal vents~\citep[e.g.,][]{Russel2010}.
...
The hydrothermal vents scenario requires a direct contact of an ocean and the planetary mantle/crust.
This requirement is not met on an ocean world with large amounts of water, where the water pressure on the ocean floor is high enough to form high-pressure ices (Noack+2016). % TODO Sleep et al., 2011? Sobotta et al., 2020?
\todo[inline]{see discussion in Kite \& Ford 2018 Sect. 6.4}
\todo[inline]{SR: The sealing away of the planetary interior from the ocean due to high-pressure ice layers is a common assumption for water world exoplanets (in addition to the references above, see e.g. Hu et al. 2021). I'm not convinced it is correct, because of relatively recent evidence showing the possibility of molecular assimitation into such ices and subsequent transport, e.g., https://iopscience.iop.org/article/10.1088/0004-637X/769/1/29/meta, https://iopscience.iop.org/article/10.3847/1538-4357/acb49a/meta, https://iopscience.iop.org/article/10.3847/1538-4357/aa5cfe/meta (I'm sure there are other workers in this area, this is just the group with which I am familiar). Exoplaneteers mostly uniformly accept this proposition, so it's not an unreasonable assumption if you want to run with it so long as its acknowledged and caveated reasonably; I'm just highlighting this for your attention so that you can make an informed decision. }

@@

%\subsection{Origins of Life Hypotheses}
...
\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/hypotheses.pdf}
        \caption{Population-level hypothesis and null hypothesis on UV irradiance derived from the cyanosulfidic scenario.}
        \label{fig:hypotheses}
    \end{centering}
\end{figure*}
Figure~\ref{fig:hypotheses} shows the hypothesis and null hypothesis derived from the predictions of the cyanosulfidic scenario.
...
